DynaProg for Scala

### 2013-01-16 docs/report/report.tex
Report first pass finished.
Nits.

@@

>>>>

\begin{verbatim}
NEW:
- CPU: Dynaprog vs ADPFusion vs RNAfold vs GAPC
- GPU: (Zuker) Dynaprog vs GAPC (si on arrive a faire marcher)
- GPU: (MatMult) Dynaprog vs ATLP
- GPU: (SWat) Dynaprog vs  CUDAlign
\begin{verbatim}

@@

 {\color{red} Size analysis to know what storage size we require: ex: Zucker requires $O(n^2)+O(n)$ storage...}

XXX: future work: proper support of two-track grammars

XXX: future work, resize tables appropriately as in GAPL.
